Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-22 Draft/Draft20181218.Rmd
Update Draft20181218.Rmd

We started with loading the needed libraries for preparation, manipulation, analysis and visualisation.  
```{r, message=FALSE, warning=FALSE}
library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
library(gridExtra)
library(lubridate)
library(plotrix)
library(treemap)
```

@@

>>>>

We started with loading the needed libraries for preparation, manipulation, analysis and visualisation.  
```{r, message=FALSE, warning=FALSE}
library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
library(gridExtra)
library(lubridate)
library(plotrix)
library(treemap)
library(cluster)
library(factoextra)
```

@@

```{r}
product_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Product_Group_Name,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

#country_Adet <-data.table::dcast(country_year, Country ~ year , value.var = c("Adet","Toplam"))

product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
   rename(Toplam_2013 = "2013") %>%
   rename(Toplam_2014 = "2014") %>%
   rename(Toplam_2015 = "2015") %>%
   rename(Toplam_2016 = "2016") %>%
   rename(Toplam_2017 = "2017")

#Normalize_product_Cluster<-product_Cluster%>%
#mutate(normalized_2013 =  round((Toplam_2013  - mean(Toplam_2013))/sd(Toplam_2013 ),2)) %>%
#mutate(normalized_2014 =  round((Toplam_2014  - mean(Toplam_2014))/sd(Toplam_2014 ),2)) %>%
#mutate(normalized_2015 =  round((Toplam_2015  - mean(Toplam_2015))/sd(Toplam_2015 ),2)) %>%
#mutate(normalized_2016 =  round((Toplam_2016  - mean(Toplam_2016))/sd(Toplam_2016 ),2)) %>%
#mutate(normalized_2017 =  round((Toplam_2017  - mean(Toplam_2017))/sd(Toplam_2017 ),2)) %>%
#select(Product_Group_Name,normalized_2013,normalized_2014,normalized_2015,normalized_2016,normalized_2017)

#set.seed(20)
#Cluster <- kmeans(Normalize_product_Cluster[, 2:6], 4, nstart = 20)

#head(Cluster)

#Normalize_product_Cluster$group<- as.factor(Cluster$cluster)

#ggplot(Normalize_product_Cluster, aes(normalized_2013,normalized_2014, color = Normalize_product_Cluster$group)) + geom_point()
#ggplot(Normalize_product_Cluster, aes(normalized_2014,normalized_2015, color = Normalize_product_Cluster$group)) + geom_point()
#ggplot(Normalize_product_Cluster, aes(normalized_2015,normalized_2016, color = Normalize_product_Cluster$group)) + geom_point()

distance <- get_dist(product_Cluster)
fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))

k2 <- kmeans(product_Cluster[, 2:6], centers = 2, nstart = 25)
str(k2)

#fviz_cluster(k2, data = product_Cluster)

set.seed(20)
Cluster <- kmeans(product_Cluster[, 2:6], 4, nstart = 20)

head(Cluster)

product_Cluster$group<- as.factor(Cluster$cluster)

ggplot(product_Cluster, aes(Toplam_2013,Toplam_2014, color = product_Cluster$group)) + geom_point()
ggplot(product_Cluster, aes(Toplam_2014,Toplam_2015, color = product_Cluster$group)) + geom_point()
ggplot(product_Cluster, aes(Toplam_2015,Toplam_2016, color = product_Cluster$group)) + geom_point()
ggplot(product_Cluster, aes(Toplam_2016,Toplam_2017, color = product_Cluster$group)) + geom_point()
